The \dealii Library, Version 9.4

### 2022-06-24 9.4/paper.tex
update table

\begin{table}
  \caption{\it Performance comparison of writing large VTU graphical output using MPI I/O on
  Frontera /scratch1/ with 16 file servers (``OSTs'') and a theoretical peak performance of 50 GB/s. ROMIO seems to enforce sequential writes when using \texttt{MPI\_File\_write\_ordered()}.}
  \label{tab:mpi-io}

@@

  \begin{tabular}{|c|c|c|c|}
  \hline
Version       & MPI routine used            & 1 file, striping 16 & 16 files, no striping \\
\hline
old VTU code  & \texttt{MPI\_File\_write\_ordered()} & 3 GB/s              & 15 GB/s              \\
new in 9.4 & \texttt{MPI\_File\_write\_at\_all()} & 17 GB/s             & 21 GB/s
\\
\hline
\end{tabular}

>>>>

\begin{table}
  \caption{\it Performance comparison of writing large VTU graphical output using MPI I/O on
  TACC Frontera /scratch1/ with 16 file servers (``OSTs'') and a theoretical peak performance of 50 GB/s. The ROMIO version used enforces sequential writes when using \texttt{MPI\_File\_write\_ordered()}.}
  \label{tab:mpi-io}

@@

  \begin{tabular}{|c|c|c|c|}
  \hline
Version       & MPI routine used            & 1 file, striping 16 & 16 files, no striping \\
\hline
\dealii{} 9.3 & \texttt{MPI\_File\_write\_ordered()} & 3 GB/s              & 15 GB/s              \\
\dealii{} 9.4 & \texttt{MPI\_File\_write\_at\_all()} & 17 GB/s             & 21 GB/s
\\
\hline
\end{tabular}
